Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-15 tuningpredictor.tex
Updates from ShareLaTeX

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphics}
\usepackage{cite}
\usepackage{rotating}
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl} 
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\rone}{\crule{1mm}{1.95mm}}
\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

Our tuning results  challenge much prior work in software analytics. 
Firstly, there exist research papers
that use data miners to   show that certain factors
are more influential than others for (say)
predicting defects. As shown below, such conclusions can be dramatically
changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
of the tuning is altered.
Hence, many old papers    need to be revisted  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
For example, one of us (Menzies) used data miners
to assert that some factors were more important than others for predicting
successful software reuse~\cite{me02k}. That assertion should now be doubted since that
Menzies study did not conduct a tuning study before reporting what factors the data miners
found where most influential.

@@

\subsection{Preliminaries}

Before beginning, we offer four caveats on these results.

Firstly, we are {\em not} saying that {\em all} learning requires
tuning. For example, when proposing fixes to software, Weimar et al. use a genetic learner
to propose patches~\cite{Weimer:2009}. Consider one performance criteria for that work; i.e. 
that   that that method can find and fix known bugs. Note that this is a {\em competency criteria}
which does not include the phrase  ``{\em better than}''. Such performance criteria do
not requiring tuning.  However, once {\em better than} enters the performance criteria
(as done in \cite{lessmann2008benchmarking,hall11,me07b,bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting})
then this becomes a race between competing methods (or attributes).  In such a race, it is unfair
to hobble one competitor with poor tunings.

Secondly, the tuning results shown here only came from one  software analytics task 
(defect prediction from static code attributes).
There are many other kinds of software analytics tasks 
(software development effort estimation, social network mining,
detecting duplicate issue reports, etc) and the implication of this
study for those tasks is unclear. 
However,  those other tasks often use the same kinds of learners
explored in this paper so it is quite possible that
the conclusions of this paper apply to other SE analytics tasks as well.

Thirdly, this paper explores {\em some} learners using {\em one}  optimizer. Hence, it makes
no claim that this is the {\em best} optimizer for {\em all} learners.
Rather, our point is that there exists at least some learners
whose performance can be dramatically improved by 
at least one simple optimization scheme.  We hope that this work inspires
much future work as this community develops and debugs best practices for tuning
software analytics.

Fourthly, it would be incorrect to say that this paper is arguing that
software analytics is somehow wrong-headed, misguided, and we should not do it anymore.
In the age of the Internet and global access to software engineering data,
there exists the  problem of information overload. {\em Something} must be done to
allow analysts to make conclusions via an automatic analysis over a lot of data.
The results of this paper is that for a particular local context
(a specific data set and a specific goal) there exists  
methods for optimizing the conclusions reached in that context.  Those conclusions
may not generalize to other contexts but this  is not a council for despair. While there may
not exist general conclusions, there does seem to exist general methods for finding
local conclusions in a particular context. Further, as shown below, those
methods may be very simple to implement and very fast to execute.

@@

One way to generate a  defect predictor from
static code is to use 
linear  regression.
This is a standard statistical
method that fits a straight line to a set of points. The line
offers a set of predicted values.
If the points are somewhat
scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
values is a measure of the error associated with that line.
Linear regression search for a line that minimizes that
error and maximizes the correlation\footnote{
$Correlation$
measures how closely two variables co-vary.  It ranges from   from -1
(perfect negative correlation) through 0 (no correlation) to +1
 (perfect positive correlation).
Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
 the number of observations and the mean of the $n$ observations, 
respectively. Then:
$S_{\mathit{PA}}=(\sum_i (p_i - \overline{p})(a_i -
  \overline{a}))/(n-1)$ and
$S_{p}=(\sum_i (p_i - \overline{p})^2)(n-1)$
and 
$S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.

@@

{\scriptsize \[
\begin{array}{l|l|ll}
\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
\mathit{LOC}   &d_i= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
\mathit{Halstead} & d_2= 0.231 + 0.00344N     \\    
                 & +  0.0009V   - 0.185L \\
                 & - 0.0343D      - 0.00541I \\
                 & + 0.000019E + 0.711B \\ 
                 &   - 0.00047T  & c_2=-0.36  
\end{array}
\]
}

\noindent
Enter tuning. Suppose the defect predictors $d_1$ and $d_2$  learned from LOC or Halstead
are used to to call an inspection
team to check for errors in certain parts of the code using the rule
\begin{equation}\label{eq:yesno}\scriptsize
\mathit{inspect}= \left\{
\begin{array}{ll}
d_i \ge T \rightarrow \mathit{Yes}\\
d_i <   T \rightarrow \mathit{No} 
\end{array}\right.
\end{equation}
\fig{pd1} shows the effects of tuning the $T$ variable. Not surprisingly,
at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
20\% at $T=0.45$ (for Halstead).

\begin{figure}[!t]
{\scriptsize
\begin{center}

@@

One  important lesson from  \fig{pd1} is that the ``best'' tunings are context
specific. For mission critical systems (e.g. a nuclear power plant), management
might accept the cost of high false alarm rates if it meant increasing the probability
of detecting errors. For such contexts, we might recommend some very small value of $T$.

The other  important lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
detector can work just as well as seemingly better ones.
Note that either the Halstead or LOC detector can reach some desired
level of recall, regardless of their correlations, just by
selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
were very similar: 14\% and 19\%).

The core point of this example is that    the true value of a detector
could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
issuing a request to an inspection team to review some module).  
This is strong motivation to explore the issue of tunings.

@@

The rest of this paper repeats the analysis of the last section, but for much
more complex learners. In those results, shown  below, we will find
examples of {\em rank reversals};
i.e.  after tuning the top ranked defector becomes last and vice versa.
Such examples motivate the extensive exploration of tuning in software analytics.
Before presenting those results, this section offers some background notes on defect prediction,
performance measures, and optimization with differential evolution.

@@

\begin{figure*}[!t]
\renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{c|l|p{4in}}
amc & average method complexity & e.g. number of JAVA byte codes\\\hline
avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
in class\\\hline
ca & afferent couplings & how many other classes use the specific
class. \\\hline
cam & cohesion amongst classes & summation of number of different
types of method parameters in every method divided by a multiplication
of number of different method parameter types in whole class and
number of methods. \\\hline
cbm &coupling between methods &  total number of new/redefined methods
to which all the inherited methods are coupled\\\hline
cbo & coupling between objects & increased when the methods of one
class access services of another.\\\hline
ce & efferent couplings & how many other classes is used by the
specific class. \\\hline
dam & data access & ratio of the number of private (protected)
attributes to the total number of attributes\\\hline
dit & depth of inheritance tree &\\\hline
ic & inheritance coupling &  number of parent classes to which a given
class is coupled (includes counts of methods and variables inherited)
\\\hline
lcom & lack of cohesion in methods &number of pairs of methods that do
not share a reference to an instance variable.\\\hline
locm3 & another lack of cohesion measure & if $m,a$ are  the number of
$methods,attributes$
in a class number and $\mu(a)$  is the number of methods accessing an
attribute,\newline
then
$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
\\\hline
loc & lines of code &\\\hline
max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
in class\\\hline
mfa & functional abstraction & number of methods inherited by a class
plus number of methods accessible by member methods of the
class\\\hline
moa &  aggregation &  count of the number of data declarations (class
fields) whose types are user defined classes\\\hline
noc &  number of children &\\\hline
npm & number of public methods & \\\hline
rfc & response for a class &number of  methods invoked in response to
a message to the object.\\\hline
wmc & weighted methods per class &\\\hline
\rowcolor{lightgray}
defect & defect & Boolean: where defects found in post-release bug-tracking systems.
\end{tabular}
}
\end{center}
\caption{OO measures used in our defect data sets.  Last line is
the dependent attribute (whether a defect is reported to  a
post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

@@

\subsubsection{Differential Evolution: The Details}

@@

DE is an evolutionary algorithm; i.e. the next {\em NewGeneration} is learnt from
a current {\em Population}.  If the new is no better than the current, then
we lose one life, terminating when we run out of lives$^5$.

Each candidate solution in the {\em Population}  
is a pair of {\em (Tunings, Scores)}. In this paper, {\em Tunings} are selected from
\fig{parameters} and {\em Scores} come from training a learner using those parameters
and applying it to some test data$^{23-28}$.

The premise of this algorithm is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$ found as follows:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates (which are generated
from the {\em Population}.

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{c c c c c c c c c c }\hline
  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
\\\hline
  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
\\  \end{tabular}
   \caption{Ratios of defective instances in each experimental data set. 
   E.g., the top left data set has 20 defective classes out of 125 total.
   This paper runs one experiment for each column
   shown in this figure. The {\em training} set is used by an untuned learner
   to build a model, which is then tested on the {\em testing} data.
   {\em Training} data is used by  differential evolution when it builds
    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
    Finally, the best model from by DE is applied to {\em testing}. 
   This information is continued  in \fig{data2}. 
   }\label{fig:data1}
\end{figure*}
\begin{figure*}[!ht]
\scriptsize
\centering
  \begin{tabular}{c c c c c c c c c c }
  \hline\hline
  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
\\\hline
  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
\\  \end{tabular}

   \caption{More ratios of  defective instances in each experimental data set. 
   Same format as \fig{data1}.}\label{fig:data2}
\end{figure*}

@@

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle.
Some of those methods have certain drawbacks:
\bi
\item  Leave-one-out is too slow for large data sets;
\item Cross-validation can mix up older and newer data sets so it may well be that
data from the {\em future} is used to test on {\em past data}.
\ei
To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.

For this experiment, we looked for data sets that had at least three  
releases in PROMISE. Note that the following ensures that all treatments 
get assessed on the same test  set.
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner.
   \item
   The {\em first} release was also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
Some data sets have more than three releases and, for those data, we could run more
 than one experiment. For example, {\em ant} has five versions in PROMISE so
 we ran three experiments called V0,V1,V2:
 \bi
 \item AntV0: first,second,third = versions 1,2,3
 \item AntV1: first,second,third = versions 2,3,4
 \item AntV2: first,second,third = versions 3,4,5
 \ei 
These data sets are displayed in \fig{data1} and \fig{data2}.

@@

Recall from Algorithm~! that we call differential evolution one time for each
goal we are trying to optimize. This section lists those optimization goals.

Let $\{A,B,C,D\}$ denote the
true negatives, 
false negatives, 
false positives, and 
true positives
(respectively) found by a binary detector. 
Certain standard measures can be computed from
$A,B,C,D$: 
\[
\begin{array}{ll}
pd=recall=&\frac{D}{B+D}\\
pf=&\frac{C}{A+C}\\
pf'=& 1 - pf\\
prec=precision=&\frac{D}{D+C}\\ 
 g = & \frac{2*pd*pf'}{pd + pf'}
\end{array}
\]
All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

The following results make no assumption that (e.g.) minimizing false alarms are 
more important that maximizing recall or precision. That determination 
should be make with respect to current business conditions:
\bi
\item
For safety critical applications, low false alarm rates are irrelevant since the cost
of overlooking any critical might outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ei
What the falling results do show is that once the optimization goal changes, so does everything
else. Hence, it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant.

@@

The introduction of this article made several claims about tuning defect predictor
that use static code attributes. This section presents
our results in order of those claims:
\be
\item Such tuning was easy (see \tion{easy});
\item Such tuning is fast (see \tion{fast});
\item Such tuning is can dramatically change the performance scores of a predictor;
e.g. one result where precision changes from 2\% to 98\% (see \tion{precision});
\item Tuning changes conclusions about what factors are most important (see \tion{import});
\item Tuning changes conclusions about what learners are better than others (see \tion{rank};)
\ee

\subsection{Tuning is Easy}

All the following results are generated with a a very simple optimizer
(differential evolution). Further, our DE  is actually much simpler
than a standard implementation. Recall from Algorithm~1 that
DE explores a {\em Population} of size {\em np=10}. This is a very small population size:
the standard recommendation is to set {\em np} to be ten times larger than the number
of attributes being optimized~\cite{stron97}

The results of this paper are presented

\section{Discussion}

\section{Related Work}

Tuning in efforts estimation, software engineering.

Defect Prediction

>>>>

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphics}
\usepackage{cite}

\usepackage{rotating}
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl} 
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
%\newcommand{\rone}{\crule{1mm}{1.95mm}}
%\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
%\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
%\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
%\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\newcommand{\rone}{}
\newcommand{\rtwo}{}
\newcommand{\rthree}{}
\newcommand{\rfour}{} 
\newcommand{\rfive}{}

@@

These results challenge much prior work. 
Firstly, there exist research papers
that use data miners to   show that certain factors
are more influential than others for (say)
predicting defects. As shown below, such conclusions can be dramatically
changed by the tuning process since those  ``influential'' factors are very different pre- and post- tuning. Also, those factors tend to  change from project to project or if the goal
of the tuning is altered.
Hence, many old papers    need to be revisted  and perhaps revised~\cite{bell2013limited,rahman2013how,me02k,moser2008comparative,zimmermann2007predicting,herzig2013predicting}.  
For example, one of us (Menzies) used data miners
to assert that some factors were more important than others for predicting
successful software reuse~\cite{me02k}. That assertion should now be doubted since that
Menzies study did not conduct a tuning study before reporting what factors the data miners
found where most influential.

@@

@@

One way to generate a  defect predictor from
static code is to use 
linear  regression.
This is a standard statistical
method that fits a straight line to a set of points. The line
offers a set of predicted values.
If the points are somewhat
scattered, then a single regression line cannot pass through all points and the distance from these predicted values to the actual
values is a measure of the error associated with that line.
Linear regression search for a line that minimizes that
error and maximizes the correlation\footnote{
{\em Correlation}
measures how closely two variables co-vary.  It ranges from   from -1
(perfect negative correlation) through 0 (no correlation) to +1
 (perfect positive correlation).
Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
 the number of observations and the mean of the $n$ observations, 
respectively. Then:
$S_{\mathit{PA}}=(\sum_i (p_i - \overline{p})(a_i -
  \overline{a}))/(n-1)$ and
$S_{p}=(\sum_i (p_i - \overline{p})^2)(n-1)$
and 
$S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.

@@

{\scriptsize \[
\begin{array}{l|l|ll}
\mathit{measures} & d= \mathit{\#defects} & \mathit{correlation}\\\hline
\mathit{LOC}   &d_1= 0.0164 +0.0114\mathit{LOC}\ & c_1 = 0.65\\\hline
\mathit{Halstead} & d_2= 0.231 + 0.00344N  +  0.0009V    \\    
                 &   - 0.185L- 0.0343D      - 0.00541I  \\ 
                 & + 0.000019E + 0.711B  - 0.00047T  & c_2=-0.36  
\end{array}
\]
}

\noindent
We now explore how tuning can alter the above  conclusion. Suppose the  predictors $d_1$ and $d_2$  learned from LOC or Halstead
are used to call an inspection
team to check for errors in   parts of the code using:
\begin{equation}\label{eq:yesno}\scriptsize
\mathit{inspect}= \left\{
\begin{array}{ll}
d_i \ge T \rightarrow \mathit{Yes}\\
d_i <   T \rightarrow \mathit{No} 
\end{array}\right.
\end{equation}
\fig{pd1} shows the effects of tuning. Not surprisingly,
at $T=0$, all modules get inspected so the false alarm rate is very high. To reduce that
problem, we can increase $T$. \fig{pd1} reports that the false alarm rate falls below
20\% at $T=0.45$ (for Halstead).

\begin{figure}[!t]

\renewcommand{\baselinestretch}{0.8}
{\scriptsize
\begin{center}

@@

One   lesson from  \fig{pd1} is that the ``best'' tunings are context
specific. For mission critical systems (e.g. a nuclear power plant), management
might accept the cost of high false alarm rates if it meant increasing the probability
of detecting errors. For such contexts, we might recommend some very small value of $T$.

The other   lesson from   \fig{pd1}  is that, with tuning, a seemingly poor
detector can work just as well as seemingly better ones.
Note that either the Halstead or LOC detector can reach some desired
level of recall, regardless of their correlations, just by
selecting the appropriate threshold value. For example, in \fig{pd1}, see the recall=75\% values
found at {\em either} $d_i\ge 0.65$ or $d_2\ge 0.45$ (and at the threshold, the false alarm rates
were very similar: 14\% and 19\%).

The  point here is that   the true value of a detector
could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
issuing a request to an inspection team to review some module).  
Hence, it is important to explore tuning
so the rest of this paper repeats the analysis of this section, but for 
more complex learners.

@@

@@

\begin{figure*}[!t]
\renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{c|l|p{4.7in}}
amc & average method complexity & e.g. number of JAVA byte codes\\\hline
avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
in class\\\hline
ca & afferent couplings & how many other classes use the specific
class. \\\hline
cam & cohesion amongst classes & summation of number of different
types of method parameters in every method divided by a multiplication
of number of different method parameter types in whole class and
number of methods. \\\hline
cbm &coupling between methods &  total number of new/redefined methods
to which all the inherited methods are coupled\\\hline
cbo & coupling between objects & increased when the methods of one
class access services of another.\\\hline
ce & efferent couplings & how many other classes is used by the
specific class. \\\hline
dam & data access & ratio of the number of private (protected)
attributes to the total number of attributes\\\hline
dit & depth of inheritance tree &\\\hline
ic & inheritance coupling &  number of parent classes to which a given
class is coupled (includes counts of methods and variables inherited)
\\\hline
lcom & lack of cohesion in methods &number of pairs of methods that do
not share a reference to an instance variable.\\\hline
locm3 & another lack of cohesion measure & if $m,a$ are  the number of
$methods,attributes$
in a class number and $\mu(a)$  is the number of methods accessing an
attribute, 
then
$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
\\\hline
loc & lines of code &\\\hline
max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
in class\\\hline
mfa & functional abstraction & number of methods inherited by a class
plus number of methods accessible by member methods of the
class\\\hline
moa &  aggregation &  count of the number of data declarations (class
fields) whose types are user defined classes\\\hline
noc &  number of children &\\\hline
npm & number of public methods & \\\hline
rfc & response for a class &number of  methods invoked in response to
a message to the object.\\\hline
wmc & weighted methods per class &\\\hline
\rowcolor{lightgray}
defect & defect & Boolean: where defects found in post-release bug-tracking systems.
\end{tabular}
}
\end{center}
\caption{OO measures used in our defect data sets.  Last line is
the dependent attribute (whether a defect is reported to  a
post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

@@

@@

DE is an evolutionary algorithm where next {\em NewGeneration} is learnt from
a current {\em Population}.  If the new is no better than  current, then
we lose one life (terminating when lives is zero)$^5$.

Each candidate solution in the {\em Population}  
is a pair of {\em (Tunings, Scores)}.  {\em Tunings} are selected from
\fig{parameters} and {\em Scores} come from training a learner using those parameters
and applying it     test data$^{23-28}$.

The premise of DE  is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates (which are generated
from the {\em Population}.

@@

@@

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle.
Some of those methods have  limitations:
\bi
\item  Leave-one-out is too slow for large data sets;
\item Cross-validation can mix up older and newer data sets so it may well be that
data from the {\em future} is used to test on {\em past data}.
\ei
To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.

For this experiment, we uses data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests.

Some data sets have more than three releases and, for those data, we could run more
 than one experiment. For example, {\em ant} has five versions in PROMISE so
 we ran three experiments called V0,V1,V2:
 \bi
 \item AntV0: first,second,third = versions 1,2,3
 \item AntV1: first,second,third = versions 2,3,4
 \item AntV2: first,second,third = versions 3,4,5
 \ei 
These data sets are displayed in \fig{data1}.

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
One style
of measure is to check the {\em variability} of that predictor.
For example,
in their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.

There exist other goals that combine defect prediction with other economic
factors.
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.

Yin et al. are concerned about
 {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
These bugs occur  when (say) developers try to fix parts of the code
where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.

In {\em Better-faster-cheaper}, we seek  project changes that lead
to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
\end{tabular}
\caption{Many ways to assess defect predictors.}\label{fig:criteria}
\end{figure}
 \begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{c c c c c c c c c c }\hline
  Dataset &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2
\\\hline
  training &20/125 &40/178 &32/293 &13/339 &216/608 &63/111 &90/272 &75/306 &79/312
\\  tuning  &40/178 &32/293 &92/351 &216/608 &145/872 &16/241 &75/306 &79/312 &48/367
\\  testing &32/293 &92/351 &166/745 &145/872 &188/965 &40/352 &79/312 &48/367 &11/492
\\ \hline
  Dataset &log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1
\\\hline
  training &34/135 &91/195 &141/237 &37/314 &16/157 &147/196 &77/162 &71/440
\\  tuning  &37/109 &144/247 &37/314 &248/385 &60/222 &142/214 &71/440 &69/453
\\  testing &189/205 &203/340 &248/385 &281/442 &86/256 &78/229 &69/453 &437/588
\\  \end{tabular}

   \caption{Ratios of defective instances in each experimental data set. 
   E.g., the top left data set has 20 defective classes out of 125 total.
   This paper runs one experiment for each column
   shown in this figure. The {\em training} set is used by an untuned learner
   to build a model, which is then tested on the {\em testing} data.
   {\em Training} data is used by  differential evolution when it builds
    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
    Finally, the best model from by DE is applied to {\em testing}.  
   }\label{fig:data1}
\end{figure*}

@@

Recall from Algorithm~1 that we call differential evolution once for each
 optimization goal. This section lists those optimization goals.

Let $\{A,B,C,D\}$ denote the
true negatives, 
false negatives, 
false positives, and 
true positives
(respectively) found by a binary detector. 
Certain standard measures can be computed from
$A,B,C,D$:

{\scriptsize\[
\begin{array}{ll}
pd=recall=&D/(B+D)\\
pf=&C/(A+C)\\
pf'=& 1 - pf\\
prec=precision=&D/(D+C) 
\end{array}
\]}

All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

The following results make no assumption that (e.g.) minimizing false alarms is 
more important than maximizing   precision. That determination 
depends on current business conditions:
\be
\item
For safety critical applications, high false alarm rates may be acceptable if the cost
of overlooking any critical can outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ee
These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
and there is insufficient space in this paper to explore all the above optimization goals.
What we can do, however, is show examples of how  changing  optimization goals can also change 
the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
but the general principle (that the search bias changes the search conclusions) would hold for all the goals
listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant (and by ``context'', we mean the optimization goal).

@@

The introduction of this article made several claims about tuning defect predictor
that use static code attributes. This section presents
support for those claims:
\be
\item  Tuning    improves the performance scores of a predictor;
e.g.  precision changes from 2\% to 98\%: see \tion{precision};
\item Tuning changes conclusions on what learners are better than others: see \tion{rank};
\item Tuning changes conclusions about what factors are most important: see \tion{import};
\item  Tuning is easy: see \tion{easy};
\item Tuning is fast: see \tion{fast};
\item Data miners should not be used ``off-the-shelf'' with their default tunings: see \tion{variance}.
\ee
